biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-09-28 paper/PaperTRA/PaperTRA.Rmd
update 1yr SE

```{r summaryall, message=FALSE, warning=FALSE}
summaryall = summary1 |> left_join(summary22) |> 
  select(c(1, 2, 6, 7, 8, 13)) |> 
  mutate(CO2eq = co2 + CO2eq,
         value1 = monet/1000 + Value, # this is NOT CORRECT, need to inflate - see original table
         value10 = monet + Value*10) |> # this is NOT CORRECT, need to deflate
  select(Estrategia, LTS, CO2eq, value1, value10)

>>>>

```{r summaryall, message=FALSE, warning=FALSE}
summaryall = summary1 |> left_join(summary22) |> 
  select(c(1, 2, 6, 7, 8, 13)) |> 
  mutate(CO2eq = co2 + CO2eq,
         value1 = monet/10 + Value, # this is NOT CORRECT, need to inflate - see original table
         value10 = monet + Value*10) |> # this is NOT CORRECT, need to deflate
  select(Estrategia, LTS, CO2eq, value1, value10)
